---
title: "A short Intro to R exploratory data analysis | exploring Kaggle State of Machine Learning Survey 2017 "
output: html_notebook

---

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
library(readxl)

library(scales)
library(DBI)

library(forcats)
#library(reshape2)
library(skimr)

```

Download data at 
https://www.kaggle.com/kaggle/kaggle-survey-2017


Load DATA
```{r}
mcr <- read.csv("/Users/merveakbas/Dropbox/_DataScience/_R/2017_NY_Rconf/multipleChoiceResponses.csv", stringsAsFactors = FALSE)
```

Check the column names
```{r}
names(mcr)
```



EXPLORE YOUR DATASET
```{r}
str(mcr)
```
Look at the first 5 rows
```{r}
head(mcr)
```

Check missing values
```{r}
mcr %>% summarize(nmissing = sum(is.na(Country)))
```

Check missing values for all variables
```{r}
mcr %>% purrr::map_df(~sum(is.na(.)))
```

Tabulate discipline1

```{r}
mcr %>% count(Country) %>% add_tally() %>% mutate(percent = (n/nn)*100)
```
Mising Value is not coded as NA
Replace empty character cells with NA

```{r}
mcr <- mcr %>%  na_if("") 
mcr %>% count(Country)
```

Check with another way
```{r}
mcr %>% summarize(nmissing = sum(is.na(Country)))
```

EXAMINE NUMERIC COLUMNS QUICKLY
```{r}
mcr %>% 
  select_if(is.numeric) %>% 
  skimr::skim()
```

EXAMINE A SINGLE COLUMN

```{r}
head(mcr$WorkMethodsSelect)
```

There are multiple answers in a character, separated by comma
We need to separate them 

```{r}
mcr %>% 
  count(WorkMethodsSelect, sort = TRUE)
```

```{r}
#add an identifier
library(dplyr)
mcr <- mcr %>% mutate(id = row_number())
```



SPLIT THE STRINGS AT COMMAS because I want to look at all methods separately

```{r}
mcr %>% mutate(workmethod = str_split(WorkMethodsSelect, ",")) %>% dplyr::select(id, workmethod)
```

Every cell is now a list - this is not very useful. 

But I want each cell of the list make one row and turn this data into a panel dataset
Use Unnest from tidyr

```{r}
library(dplyr)
mcr %>%  unnest( workmethods= str_split(WorkMethodsSelect, ",")) %>% dplyr::select(id, workmethods)
```

Or another way of doing it
```{r}

unnested_methods <- mcr %>% mutate(workmethods= str_split(WorkMethodsSelect, ",")) %>% dplyr::select(id, workmethods) %>% unnest()
unnested_methods
```

```{r}
unnested_methods %>% count(workmethods) %>% ggplot(aes(x = workmethods, y = n)) + geom_col()
```

UGLY - We better transpose it and make the bars sideways
```{r}
library(forcats)
unnested_methods %>% count(workmethods) %>% ggplot(aes(x = workmethods, y = n)) + geom_col() + coord_flip()
```

Let's sort it 

```{r}
library(forcats)
unnested_methods %>% count(workmethods) %>% ggplot(aes(x = fct_reorder(workmethods, n), y = n)) + geom_col() + coord_flip()

```





